The title

### 2020-07-29 manuscript/manuscript.Rmd
behavior first

@@

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists('output/exp1-epo.fif'):
  # Load preprocessed data from file
  epochs_exp1 = mne.read_epochs('output/exp1-epo.fif', preload=True)
else:
  # Actually apply the preprocessing function
  epochs_exp1 = [preproc(fname, **preproc_params) for fname in fnames_exp1]
  # Combine into a single data set
  epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
  # Backup epochs to the export folder
  epochs_exp1.save('output/exp1-epo.fif')

# Get indices of bad epochs despite ICA
rej_exp1 = epochs_exp1.copy().drop_bad(reject=reject).drop_log
rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
```

```{r exp1-analysis}
# Define function for processing behavioral data
preproc_behav <- function(txt_fname){
  # Read log file
  dat <-  suppressMessages(suppressWarnings(read_tsv(txt_fname)))
  # Remove filler stimuli (well-known objects)
  dat %<>% filter(bek_unbek != "bekannt")
  # Add a column for the part of the experiment
  dat %<>% mutate(part = as_factor(Wdh - 210))

  # Assign stimuli to conditions based on keywords and button presses
  known <- dat %>% filter(part == "1" & Tastencode == 201) %>% pull(StimID)
  insight <- dat %>%filter(part == "2" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>% pull(StimID)
  naive <- dat %>% filter(part == "2" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>% pull(StimID)
  dat %<>% mutate(condition = as_factor(case_when(StimID %in% known ~ "Known",
                                                  StimID %in% insight ~ "Insight",
                                                  StimID %in% naive ~ "Naive")))
  # Remove unrealistically short RTs
  dat %<>% mutate(RT = replace(RT, RT < 200, NA))
  return(dat)}

>>>>

```{r exp1-behavior}
# Define function for processing behavioral data
preproc_behav <- function(txt_fname){
  # Read log file
  dat <-  suppressMessages(suppressWarnings(read_tsv(txt_fname)))
  # Remove filler stimuli (well-known objects)
  dat %<>% filter(bek_unbek != "bekannt")
  # Add a column for the part of the experiment
  dat %<>% mutate(part = as_factor(Wdh - 210))
  # Assign stimuli to conditions based on keywords and button presses
  known <- dat %>% filter(part == "1" & Tastencode == 201) %>% pull(StimID)
  insight <- dat %>%filter(part == "2" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>% pull(StimID)
  naive <- dat %>% filter(part == "2" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>% pull(StimID)
  dat %<>% mutate(condition = as_factor(case_when(StimID %in% known ~ "Known",
                                                  StimID %in% insight ~ "Insight",
                                                  StimID %in% naive ~ "Naive")))
  # Remove unrealistically short RTs
  dat %<>% mutate(RT = replace(RT, RT < 200, NA))
  return(dat)}

# Select only relevant columns
data_exp1 %<>% select(part, condition, participant, item, RT)

# Tell MNE to exclude trials without a proper condition or RT
data_exp1 %<>% mutate(condition = replace(condition, condition == "Known" | is.na(RT), NA)) %>%
  mutate(condition = fct_explicit_na(condition, na_level = "Exclude")) %>% droplevels()
```

@@

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists('output/exp1-epo.fif'):
  # Load preprocessed data from file
  epochs_exp1 = mne.read_epochs('output/exp1-epo.fif', preload=True)
else:
  # Actually apply the preprocessing function
  epochs_exp1 = [preproc(fname, **preproc_params) for fname in fnames_exp1]
  # Combine into a single data set
  epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
  # Add metadata from R
  epochs_exp1.metadata = r.data_exp1
  # Backup epochs to the export folder
  epochs_exp1.save('output/exp1-epo.fif')

# Remove trials with invalid condition or RTs
epochs_exp1 = epochs_exp1['condition != "Exclude"']

# # Compute evoked potentials for each part x condition
# evokeds_exp1 = dict()
# for pt in ['1', '2', '3']:
#   for cn in ['Insight', 'Naive']:
#     query = 'part == "' + pt + '" and condition == "' + cn + '"'
#     evokeds_exp1['Part' + pt + '_' + cn] = epochs_exp1[query].average()
# mne.viz.plot_compare_evokeds(evokeds_exp1, cmap=('condition', 'viridis'), picks='P8')

# # Get indices of bad epochs despite ICA
# rej_exp1 = epochs_exp1.copy().drop_bad(reject=reject).drop_log
# rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
# rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
```

```{r exp1-analysis}
